Dynamical Properties of Molecular Cloud Complexes in Galaxies at the Epoch of Reionization

### 2019-07-04 WRITEUP/ms.tex

While the virial parameter defined as Equation~\ref{eqn:alpha} is typically used in observational studies, as they are designed to probe structures that are composed of mainly molecular gas only, we calculate the virial parameter of MCCs including the influence from the stellar component (i.e., $\alpha_{\rm vir, tot}$ via Equation~\ref{eqn:alpha_tot}) given the high stellar-to-gas mass ratios of some molecular structures identified (see \Fig{stellarRatio16}).
%
The biggest MCC identified at low $n_{\rm cut}$ and with the highest stellar-to-gas mass ratio ($\gtrsim$\,1; \Fig{stellarRatio16}) corresponds to the central main disk of \flower (see top panels of \Fig{MCC} and \Sec{distribution}). The large amount of stellar mass already assembled in \flower explains the low {\em total} virial parameter seen in the middle left panel of \Fig{larsons_single}, where the stellar gravitational potential influences the overall stability. On the other hand, the MCCs in this phase are mostly stable, with virial parameter comparable to some of the molecular structures observed in the Milky Way, though the MCCs are more massive.

@@

\AP{let us recall to make the not about different molecular tracers also here}
We investigate possible variations in the dynamics of the molecular structures of \flower by adopting different values of $n_{\rm cut}$ to test the robustness of our results against the choice of density threshold. That is, how sensitively are the structure properties, and thus, the results presented in \Sec{singless}, dependent on the choice of density thresholds?

@@

In this section, we compare the observable quantities of MCCs obtained from the simulations (e.g., $\sigma_{\rm gas}$, $R$, $M_{\rm gas}$, $\Sigma_{\rm gas}$) with those of molecular gas structures from \obs at lower redshift.
%
The velocity dispersion of MCCs in \flower is similar to those observed in $z$\ssim2 spatially resolved studies of gas-rich star-forming galaxies, spanning a range of $\sigma_{\rm gas}\simeq$\,20$-$80\,\kms (\Fig{larsons_single}; see e.g., \citealt{Swinbank11a}). However, the sizes of MCCs are almost a factor of two smaller. This suggests that the sizes of \highz molecular gas structures reported in the literature are probably limited by the spatial resolution.
%
The velocity dispersions of some MCCs are also comparable to the most turbulent gas clouds observed in the inner Milky way and nearby gas-rich galaxies (e.g., M64; \citealt{Oka01a, Rosolowsky05a, Heyer09a, Leroy15a}), which lie along the locus of $\sigma_{\rm gas}\propto R^{0.56}$. Such high velocity dispersion in \flower is dominated by non-thermal energy (\Fig{vv}) and results from the injection of kinetic energy from recent \SF as \flower is assembling its stellar mass (given the high Mach numbers of MCCs; \Sec{distribution}). In fact, by the accreting stage (see \Fig{SFH}a) at $z\simeq$\,7.2, \flower has assembled a stellar mass of $M_\star$\eq7.5\E{9}\,\Msun.
%
This contrasts with \citet{Krumholz18a}, who show that numerical models and analytic arguments point to feedback generally not being able to produce velocity dispersions of more than 10--20 km~s$^{-1}$, with higher velocities likely being produced by Toomre instability driven radial inflow.

@@

This also implies that \obs on spatially resolution better than $\simeq$40\,pc are needed to examine the truly star-forming structures (cores), and thus, \SF in the first galaxies. Such resolution is in principle within reach using ALMA, for which 0\farcs01 resolution images can be attained using the high frequency bands. 
%
With the Next Generation VLA (ngVLA), which is approximately ten times more sensitive than ALMA, direct observations of molecular gas clouds in galaxies at the EoR on cloud scales will be possible via the higher-$J$ rotational transitions of CO in the 2030s.
% 0.005" highest freq
In the meantime, cosmological zoom-in simulations, such as \ncode{Serra}, while inherently limited in galaxy statistics and are subject to the sub-grid models adopted, serve as a useful tool for examining and making predictions on the morphology and dynamics of the molecular ISM of the first galaxies.

%==============================================================================
%                                Back matters
%==============================================================================
% ACKNOWLEDGEMENTS
%-------------------------------------
% \acknowledgements

>>>>

While the virial parameter defined as Equation~\ref{eqn:alpha} is typically used in observational studies, as they are designed to probe structures that are composed of mainly molecular gas only, we calculate the virial parameter of MCCs including the influence from the stellar component (i.e., $\alpha_{\rm vir, tot}$ via Equation~\ref{eqn:alpha_tot}) given the high stellar-to-gas mass ratios of some molecular structures identified (see \Fig{stellarRatio16}).
%
The biggest MCC identified at low $n_{\rm cut}$ and with the highest stellar-to-gas mass ratio ($\gtrsim$\,1; \Fig{stellarRatio16}) corresponds to the central main disk of \flower (see top panels of \Fig{MCC} and \Sec{distribution}). The large amount of stellar mass already assembled in \flower explains the low {\em total} virial parameter seen in the middle left panel of \Fig{larsons_single}, where the stellar gravitational potential influences the overall stability. On the other hand, the MCCs in this phase are mostly stable\footnote{We check that the gas-only virial parameter of MCCs is comparable to the {\em total} virial parameter.}, with virial parameter comparable to some of the molecular structures
observed in the Milky Way, though the MCCs are more massive.

@@

\AP{let us recall to make the not about different molecular tracers also here}

We investigate possible variations in the dynamics of the molecular structures of \flower by adopting different values of $n_{\rm cut}$ to test the robustness of our results against the choice of density threshold.
That is, how sensitively are the structure properties, and thus, the results presented in \Sec{singless}, dependent on the choice of density thresholds?

@@

In this section, we compare the observable quantities of MCCs obtained from the simulations (e.g., $\sigma_{\rm gas}$, $R$, $M_{\rm gas}$, $\Sigma_{\rm gas}$) with those of molecular gas structures from \obs at lower redshift.
%
The velocity dispersions of some MCCs are also comparable to the most turbulent gas clouds observed in the inner Milky way and nearby gas-rich galaxies (e.g., M64; \citealt{Oka01a, Rosolowsky05a, Heyer09a, Leroy15a}), which lie along the locus of $\sigma_{\rm gas}\propto R^{0.56}$. Such high velocity dispersion in \flower is dominated by non-thermal energy (\Fig{vv}) and results from the injection of kinetic energy from recent \SF as \flower is assembling its stellar mass (given the high Mach numbers of MCCs; \Sec{distribution}). In fact, by the accreting stage (see \Fig{SFH}a) at $z\simeq$\,7.2, \flower has assembled a stellar mass of $M_\star$\eq7.5\E{9}\,\Msun.

This contrasts with \citet{Krumholz18a}, who show that numerical models and analytic arguments point to feedback generally not being able to produce velocity dispersions of more than 10--20 km~s$^{-1}$, with higher velocities likely being produced by Toomre instability driven radial inflow.

@@

This also implies that \obs on spatially resolution better than $\simeq$40\,pc are needed to examine the truly star-forming structures (cores), and thus, \SF in the first galaxies. Such resolution is in principle within reach using ALMA, for which 0\farcs01 resolution images can be attained using the high frequency bands. With the Next Generation VLA (ngVLA\footnote{\url{http://library.nrao.edu/public/memos/ngvla/NGVLA\_21.pdf}}), which is approximately ten times more sensitive than ALMA, direct observations of molecular gas clouds in galaxies at the EoR on cloud scales will be possible via the higher-$J$ rotational transitions of CO in the 2030s.
% 0.005" highest freq
In the meantime, cosmological zoom-in simulations, such as \ncode{Serra}, while inherently limited in galaxy statistics and are subject to the sub-grid models adopted, serve as a useful tool for examining and making predictions on the morphology and dynamics of the molecular ISM of the first galaxies.

%-------------------------------------------------------
%                                Back matters
%-------------------------------------------------------
% ACKNOWLEDGEMENTS
%-------------------------------------
% \acknowledgements
